An R Markdown document converted from "12_EthnicAssoc.ipynb

### 2025-11-12 scripts/14_Rebuttal.Rmd

```{r}
cluscolmap <- validclusmod %>%
    transmute(
        clusmod = map(clusmod, select, Cluster = validclus_name, W = validclus_weights)
    ) %>%
    unnest(clusmod) %>%
    group_by(Cluster) %>%
    summarise(W2 = exp(sum(log((W))))) %>%
    arrange(-W2) %>%
    mutate(
        Cluster = factor(Cluster, levels = Cluster),
        ClusCol = scales::hue_pal()(n())
    )
cluscolmap
```

```{r}
options(repr.plot.res = 300, repr.plot.width = 6, repr.plot.height = 3)
tsne %>%
    map("Y") %>%
    imap(~data.frame(.x, maxprobdat[[.y]])) %>%
    bind_rows(.id = "sex") %>%
    filter(Prob >= .95) %>%
    ggplot(aes(X1, X2)) +
    geom_point(aes(color = Cluster), shape = ".", alpha = .1) +
    scale_color_discrete(
        guide = guide_legend(
            override.aes = list(shape = 19, alpha = 1)
        )
    ) +
    facet_grid(~sex) +
    theme_bw() +
    labs(x = "t-SNE dim 1", y = "t-SNE dim 2")
```

```{r}
cv_kpc <- map(
    1:5,
    function(cvn){
        set.seed(cvn)
        SAMP <- sample(60000, 10000)
        map(
            residtab,
            function(x){
                mod <- kernlab::kpca(
                    x = ~.,
                    data = x[SAMP,-1],
                    kernel = "rbfdot",
                    features = 2
                )
                kernlab::predict(mod, x[,-1])
            }
        )
    }
)
```

```{r}
cvkpcres <- cv_kpc %>%
    map(
        function(CVS){
            imap(
                CVS,
                function(DAT, SEX){
                    tibble(data.frame(DAT, maxprobdat[[SEX]]))
                }
            ) %>%
            bind_rows(.id = "sex")
        }
    ) %>%
    bind_rows(.id = "cvn")
head(cvkpcres)
```

```{r}
options(repr.plot.res = 300, repr.plot.width = 8, repr.plot.height = 3)
cvkpcres %>%
    ggplot(aes(X1, X2)) +
    geom_point(aes(color = Cluster), shape = ".", alpha = .1) +
    scale_color_discrete(
        guide = guide_legend(
            override.aes = list(shape = 19, alpha = 1)
        )
    ) +
    facet_grid(sex~cvn) +
    theme_bw() +
    labs(x = "PC1", y = "PC2")
```

## Colinearity across variables

```{r}
strat_dat %>%
    bind_rows %>%
    count(age <= 50) %>%
    mutate(prop = round(100*n/sum(n), 2))
```

```{r}
corsig <- strat_dat %>%
    map(select, -c(eid, sex, age, bmi, smoking)) %>%
    map(cor) %>%
    map(~{.x[lower.tri(.x, diag = TRUE)] <- NaN;.x}) %>%
    map(reshape2::melt, na.rm = TRUE) %>%
    bind_rows(.id = "sex") %>%
    group_by(Var1, Var2) %>%
    filter(any(abs(value) > 0.2)) %>%
    ungroup %>%
    pivot_wider(names_from = sex, names_prefix = "bf_")
corsig
```

```{r}
residtab %>%
    map(select, sbp, dbp, whr, alt, crp, hdl, tg, ldl) %>%
    map(cor) %>%
    map(~{.x[lower.tri(.x, diag = TRUE)] <- NaN;.x}) %>%
    map(reshape2::melt, na.rm = TRUE) %>%
    bind_rows(.id = "sex") %>%
    pivot_wider(names_from = sex, names_prefix = "af_") %>%
    inner_join(corsig) %>%
    transmute(
        across(starts_with("Var")),
        across(c(bf_Female, af_Female), \(x) round(x, digits = 2)),
        across(c(bf_Male, af_Male), \(x) round(x, digits = 2))
    )
```

```{r}
hclustdat <- residtab %>%
    map(select, -eid, -dbp) %>%
    map(as.matrix) %>%
    map(ClustOfVar::hclustvar)
```

```{r}
hclustdat <- residtab %>%
    map(select, -eid) %>%
    map(cor) %>%
    map(~as.dist(1 - .x)) %>%
    map(hclust, method = "single")
```

```{r}
plot(hclustdat$Female)
```

```{r}
plot(hclustdat$Male)
```

```{r}
pcdat <- residtab %>%
    map(~prcomp(.x[,-1]))
```

```{r}
options(repr.plot.res = 300, repr.plot.width = 8, repr.plot.height = 3)
pcdat %>%
    map(~{
        eigs <- .x$sdev^2
        tibble(X = paste0("PC", 1:length(eigs)),
               VarExp = eigs / sum(eigs))
    }) %>%
    bind_rows(.id = "sex") %>%
    ggplot(aes(reorder(X, desc(VarExp)), 100*VarExp)) +
    geom_col() +
    #geom_hline(yintercept = 95, lty = "dashed", color = "red") +
    facet_grid(~sex) +
    theme_bw() +
    labs(x = NULL, y = "%VarExp")
```

```{r}
options(repr.plot.res = 300, repr.plot.width = 8, repr.plot.height = 3)
pcdat %>%
    map(~{
        eigs <- .x$sdev^2
        tibble(X = paste0("PC", 1:length(eigs)),
               VarExp = eigs / sum(eigs)) %>%
        mutate(CumVarExp = cumsum(VarExp))
    }) %>%
    bind_rows(.id = "sex") %>%
    ggplot(aes(reorder(X, desc(VarExp)), 100*CumVarExp)) +
    geom_col() +
    geom_hline(yintercept = 90, lty = "dashed", color = "red") +
    facet_grid(~sex) +
    theme_bw() +
    labs(x = NULL, y = "Cumulative\n%VarExp")
```

```{r}
pcumap <- map(
    pcdat,
    ~uwot::umap(
        X = .x$x[,1:8],
        n_components = 2, 
        n_neighbors = max(10, round(10 + 15 * (log10(nrow(.x$x) - 4)))), 
        nn_method = "annoy", n_trees = 100, n_sgd_threads = "auto", 
        init = "pca", n_epochs = 500, approx_pow = TRUE,
        binary_edge_weights = TRUE, dens_scale = 1, 
        ret_extra = c("model", "fgraph"), verbose = FALSE       
    )
)
```

```{r}
cluscolmap
```

```{r}
options(repr.plot.res = 300, repr.plot.width = 7, repr.plot.height = 4)
pcumap %>%
    map("embedding") %>%
    map(data.frame) %>%
    map2(maxprobdat, bind_cols) %>%
    bind_rows(.id = "sex") %>%
    filter(Prob > .8) %>%
    mutate(Cluster = gsub("prob", "", Cluster)) %>%
    ggplot(aes(X1, X2)) +
    geom_point(aes(color = Cluster), alpha = .1, shape = ".") +
    scale_alpha_identity() +
    scale_color_manual(
        values = setNames(
            cluscolmap$ClusCol,
            cluscolmap$Cluster
        ),
        guide = guide_legend(
            override.aes = list(shape = 19, alpha = 1)
        )
    ) +     
    facet_wrap(~sex) +
    theme_bw() +
    labs(x = "UMAP1", y = "UMAP2")
```

```{r}
validclusmod %>%
    transmute(
        sex,
        modularity = map2_dbl(
            umapmod, maxprobdat,
            ~{
                Gr <- igraph::graph_from_adjacency_matrix(
                    .x$fgraph, mode = "undirected"
                )
                memb <- as.numeric(factor(.y$Cluster))
                igraph::modularity(Gr, memb)
            }   
        )
    )
```

```{r}
pcumap %>%
    imap(
        ~{
            Gr <- igraph::graph_from_adjacency_matrix(
                .x$fgraph, mode = "undirected"
            )
            MAXPROB <- maxprobdat[[.y]]
            igraph::V(Gr)$name <- 1:nrow(MAXPROB)
            MAXPROB %>%
                mutate(eid = row_number()) %>%
                nest(DAT = -Cluster) %>%
                transmute(
                    Cluster,
                    tval = map_dbl(
                        DAT,
                        function(XCL){
                            clusGr <- igraph::induced_subgraph(Gr, as.character(XCL$eid))
                            igraph::transitivity(clusGr)
                        }
                    )
                )
        }
    )
```

```{r}
pcclusparams <- pcdat %>%
    map2(
        probdfs, 
        function(PCD, PRB){
            apply(
                PRB, 2, 
                function(clus){
                    cov.wt(
                        x = PCD$x[,1:8], 
                        wt = clus
                    )
                }
            )
        }
    )
```

```{r}
coord_straightpolar <- function(theta = 'x', start = 0, direction = 1, clip = "on") {
  theta <- match.arg(theta, c("x", "y"))
  r <- if (theta == "x") 
    "y"
  else "x"
  ggproto(NULL, CoordPolar, theta = theta, r = r, start = start,
          direction = sign(direction), clip = clip,
          # This is the different bit
          is_linear = function(){TRUE})
}
```

```{r}
pcclusparams %>%
    map(map, "center") %>%
    map(
        map, 
        ~tibble(
            VAR = names(.x), 
            value = .x
        )
    ) %>%
    map(bind_rows, .id = "Cluster") %>%
    bind_rows(.id = "sex") %>%
    ggplot(aes(VAR, value)) +
    geom_polygon(
        group = 1, 
        color = "blue",
        linewidth = .2,
        fill = alpha("grey", .25)
    ) +
    geom_point(size = .25) +
    coord_straightpolar(theta = "x") +
    facet_grid(sex ~ Cluster) +
    theme_bw()
```

```{r}
pcprobs <- imap(
    pcdat,
    function(PCD, SEX){
        DAT <- PCD$x[,1:8]
        PCL <- pcclusparams[[SEX]]
        MUs <- map(PCL, "center")
        COVMATs <- map(PCL, "cov")
        W <- validclusmod$clusmod[
            validclusmod$sex == SEX
        ][[1]]$validclus_weights
        pdfs <- mapply(
            function(mu, covmat){ mvtnorm::dmvnorm(DAT, mu, covmat) },
            MUs, COVMATs
        )
        L <- pdfs %*% diag(W)
        colnames(L) <- names(PCL)
        tibble(data.frame(L / rowSums(L)))
    }
)
```

```{r}
pcprobs$Female %>% head
```

```{r}
pcprobs %>%
    map(
        ~{
            pp <- pmax(as.matrix(.x), .Machine$double.xmin)
            ent <- -sum(pp * log(pp))
            1 - ent / (nrow(pp) * log(ncol(pp)))
        }
    )
```

```{r}
gausmixres <- pcdat %>% 
    map(
        ~mclust::mclustBIC(data = .x$x[,1:8], G = 1:20, modelNames = "VVV")
    )
```

```{r}
options(repr.plot.height = 3, repr.plot.width = 7)
gausmixres %>%
    map(
        ~data.frame(
            Nclus = 1:20,
            BIC = .x[,1]
        )
    ) %>%
    bind_rows(.id = "sex") %>%
    ggplot(aes(Nclus, BIC)) +
    geom_line() +
    geom_point() +
    facet_wrap(~sex, scales = "free") +
    theme_bw()
```

```{r}
gmbest <- pcdat %>% 
    map(
        ~{
            mclustBIC <- mclust::mclustBIC
            mclust::Mclust(.x$x[,1:8], G = 4, modelNames = "VVV")
        }
    )
```

```{r}
gmbest %>%
    map(
        ~{
            pp <- pmax(as.matrix(.x$z), .Machine$double.xmin)
            ent <- -sum(rowSums(pp * log(pp)))
            1 - ent / (nrow(pp) * log(ncol(pp)))
        }
    ) %>%
    map(round, 2)
```

```{r}
gpairs_lower <- function(g){
  g$plots <- g$plots[-(1:g$nrow)]
  g$yAxisLabels <- g$yAxisLabels[-1]
  g$nrow <- g$nrow -1

  g$plots <- g$plots[-(seq(g$ncol, length(g$plots), by = g$ncol))]
  g$xAxisLabels <- g$xAxisLabels[-g$ncol]
  g$ncol <- g$ncol - 1

  g
}
```

```{r}
pcdat %>%
    map("x") %>%
    map_dbl(~max(abs(.x))) %>%
    max %>%
    round
```

```{r}
options(repr.plot.height = 1, repr.plot.width = 10)
cluscolp <- cluscolmap %>%
    ggplot(aes(Cluster, W2, color = Cluster)) +
    geom_point() +
    scale_color_discrete(
        guide = guide_legend(
            position = "top",
            direction = "horizontal",
            nrow = 1
        )
    ) +
    theme_bw()
cluscolguide <- GGally::grab_legend(cluscolp)
cluscolguide
```

```{r}
GPointsUpper <- function(data, mapping, ...){
    GGally::ggally_points(data, mapping, ...) +
    scale_color_manual(
            values = setNames(
                cluscolmap$ClusCol,
                cluscolmap$Cluster
            )
    ) +
    scale_x_continuous(
        limits = c(-10,10),
        breaks = c(-5, 0, 5)
    ) +
    scale_y_continuous(
        limits = c(-10,10),
        breaks = c(-5, 0, 5)
    )
}
GPointsLower <- function(data, mapping, ...){
    GGally::ggally_points(data, mapping, ...) +
    scale_x_continuous(
        limits = c(-10,10),
        breaks = c(-5, 0, 5)
    ) +
    scale_y_continuous(
        limits = c(-10,10),
        breaks = c(-5, 0, 5)
    )
}
GDiagFx <- function(data, mapping, ...){
    GGally::ggally_densityDiag(data, mapping, ...) +
    scale_x_continuous(
        limits = c(-10,10),
        breaks = c(-5, 0, 5)
    ) +
    theme(
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank()
    )
}
```

```{r}
g <- pcdat %>%
    map("x") %>%
    map(data.frame) %>%
    map2(maxprobdat, bind_cols) %>%
    map(mutate, Cluster = gsub("prob", "", Cluster)) %>%
    map(
        GGally::ggpairs,
        columns = 1:10,
        mapping = aes(color = Cluster),
        lower = list(
            continuous = GGally::wrap(
                GPointsUpper,
                shape = ".", alpha = .1
            )
        ),
        diag = list(
            continuous = GGally::wrap(
                GDiagFx,
                color = "black", fill = "grey",
                linewidth = .1
            )
        ),
        upper = list(
            continuous = GGally::wrap(
                GPointsLower, 
                color = "black", 
                shape = ".", alpha = .1
            )
        )
    ) %>%
    map(
        ~.x +
        theme(
            axis.text = element_text(size = 4),
            axis.ticks = element_line(linewidth = .1),
            strip.text = element_text(size = 6),
            panel.spacing = unit(0, "mm"),
            panel.border = element_rect(colour = "black", fill = NA),
            strip.background = element_rect(colour = "black", fill = NA)
        )
    ) %>%
    map(GGally::ggmatrix_gtable) %>%
    map(patchwork::wrap_elements) %>%
    patchwork::wrap_plots(nrow = 1)
```

```{r}
options(repr.plot.height = 5, repr.plot.width = 10)
patchwork::wrap_plots(
    cluscolguide, g,
    ncol = 1,
    heights = c(.01,.99)
)
```

```{r}
exdat_dhg <- pmap(
    list(
        strat_dat,
        residtab,
        probdfs
    ),
    function(ORIG, RESID, PROB){
        tibble(
            BMI = ORIG$bmi,
            FGres = RESID$fg,
            DHG = PROB$probDHG,
            BC = PROB$probBC
        )
    }
) %>%
    bind_rows(.id = "sex")
head(exdat_dhg)
```

```{r}
cluscolmap
```

```{r}
options(repr.plot.height = 5, repr.plot.width = 10)
dhgres <- exdat_dhg %>%
    ggplot(aes(BMI, FGres)) +
    geom_point(aes(color = DHG), size = .25) +
    scale_color_gradient(
        low = alpha(
            cluscolmap$ClusCol[
                cluscolmap$Cluster == "DHG"
            ], 
            0
        ),
        high = cluscolmap$ClusCol[
            cluscolmap$Cluster == "DHG"
        ]
    ) +
    ggdensity::geom_hdr() +
    geom_hline(yintercept = 0, lty = "dashed") +
    facet_grid(~sex) +
    theme_bw() +
    labs(
        x = NULL, y = "FG\nstandardised\nresiduals",
        color = "DHG\nprobability",
        alpha = "Overall\ndensity"
    ) +
    theme(
        strip.text.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.x = element_blank()
    )
dhgres
```

```{r}
wtd_quantile <- function(x, p, q){
    n <- sum(p)
    indexes <- order(x)
    x <- x[indexes]
    p <- p[indexes]
    p <- p / n
    cdfprobs <- cumsum(c(0, p))
    sapply(
        setNames(q, q), 
        function(QUANTILE) {
            Q <- pbeta(cdfprobs, n * QUANTILE, n * (1 - QUANTILE))
            W <- tail(Q, -1) - head(Q, -1)
            sum(W * x)
        }
    )
}
```

```{r}
options(repr.plot.height = 1, repr.plot.width = 10)
boxpld <- exdat_dhg %>%
    pivot_longer(
        c(DHG, BC), 
        names_to = "Cluster",
        values_to = "Prob"
    ) %>%
    nest(D = -c(sex, Cluster)) %>%
    mutate(
        D = map(
            D,
            ~wtd_quantile(
                .x$BMI, .x$Prob, 
                c(.025, .25, .5, .75, .975)
            )
        ),
        D = map(D, ~tibble(name = names(.x), value = .x))
    ) %>%
    unnest(D) %>%
    pivot_wider(names_prefix = "p")
boxpld
```

### 2025-11-12 scripts/14_Rebuttal.Rmd

```{r}
options(repr.plot.height = 1, repr.plot.width = 10)
bx1 <- boxpld %>%
    filter(Cluster == "DHG") %>%
    ggplot(aes(y = "DHG")) +
    geom_boxplot(
        aes(
            xmin = p0.025,
            xlower = p0.25,
            xmiddle = p0.5,
            xupper = p0.75,
            xmax = p0.975
        ),
        stat = "identity",
        fill = cluscolmap$ClusCol[
            cluscolmap$Cluster == "DHG"
        ]
    ) +
    facet_grid(~sex) +
    coord_cartesian(
        xlim = c(
            min(exdat_dhg$BMI),
            max(exdat_dhg$BMI)
        )
    ) +
    labs(x = NULL, y = NULL) +
    theme_bw() +
    theme(
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.text.y = element_text(face = "bold"),
        plot.margin = margin()
    )
bx1
```

```{r}
options(repr.plot.height = 1, repr.plot.width = 10)
bx2 <- boxpld %>%
    filter(Cluster == "BC") %>%
    ggplot(aes(y = "BC")) +
    geom_boxplot(
        aes(
            xmin = p0.025,
            xlower = p0.25,
            xmiddle = p0.5,
            xupper = p0.75,
            xmax = p0.975
        ),
        stat = "identity",
        fill = cluscolmap$ClusCol[
            cluscolmap$Cluster == "BC"
        ]
    ) +
    facet_grid(~sex) +
    coord_cartesian(
        xlim = c(
            min(exdat_dhg$BMI),
            max(exdat_dhg$BMI)
        )
    ) +
    labs(x = "BMI (kg/m2)", y = NULL) +
    theme_bw() +
    theme(
        strip.text.x = element_blank(),
        axis.text.y = element_text(face = "bold"),
        plot.margin = margin()
    )
bx2
```

```{r}
options(repr.plot.height = 5, repr.plot.width = 10)
patchwork::wrap_plots(
    bx1,
    patchwork::plot_spacer(),
    dhgres +
    geom_vline(
        data = filter(boxpld, Cluster == "BC"),
        aes(xintercept = p0.5),
        color = cluscolmap$ClusCol[
            cluscolmap$Cluster == "BC"
        ]
    ) +
    geom_vline(
        data = filter(boxpld, Cluster == "DHG"),
        aes(xintercept = p0.5),
        color = cluscolmap$ClusCol[
            cluscolmap$Cluster == "DHG"
        ]
    ),
    patchwork::plot_spacer(),
    bx2,
    ncol = 1,
    heights = c(.05, -0.04, .9, -0.04, .05)
)
```

```{r}
options(repr.plot.height = 4, repr.plot.width = 15)
strat_dat %>%
    map(select, eid, all_of(BIOMARKERS)) %>%
    map(pivot_longer, -eid) %>%
    bind_rows(.id = "sex") %>%
    ggplot(aes(value)) +
    geom_density() +
    ggh4x::facet_grid2(sex ~ name, scales = "free", independent = "all") +
    theme_bw()
```

```{r}
options(repr.plot.height = 4, repr.plot.width = 15)
logtrdat <- strat_dat %>%
    map(mutate, across(.cols = c(alt, crp, tg, fg, scr), .fns = log))
map(logtrdat, head)
```

```{r}
logtrdat %>%
    map(select, eid, all_of(BIOMARKERS)) %>%
    map(pivot_longer, -eid) %>%
    bind_rows(.id = "sex") %>%
    ggplot(aes(value)) +
    geom_density() +
    ggh4x::facet_grid2(sex ~ name, scales = "free", independent = "all") +
    theme_bw()
```

```{r}
residlogtrdat <- logtrdat %>% 
    map(
        ~sapply(
            select(.x, all_of(BIOMARKERS)),
            function(X){
                lm(X ~ .x$age + .x$bmi + .x$smoking) %>%
                    resid %>%
                    scale %>%
                    as.vector
            }
        )
    )
map(residlogtrdat, head)
```

```{r}
logumap <- map(
    residlogtrdat,
    ~uwot::umap(
        X = .x,
        n_components = 2, 
        n_neighbors = max(10, round(10 + 15 * (log10(nrow(.x) - 4)))), 
        nn_method = "annoy", n_trees = 100, n_sgd_threads = "auto", 
        init = "pca", n_epochs = 500, approx_pow = TRUE,
        binary_edge_weights = TRUE, dens_scale = 1, 
        ret_extra = c("model", "fgraph"), verbose = FALSE       
    )
)
```

```{r}
options(repr.plot.res = 300, repr.plot.width = 7, repr.plot.height = 4)
logumap %>%
    map("embedding") %>%
    map(data.frame) %>%
    map2(maxprobdat, bind_cols) %>%
    bind_rows(.id = "sex") %>%
    mutate(Cluster = gsub("prob", "", Cluster)) %>%
    ggplot(aes(X1, X2)) +
    geom_point(aes(color = Cluster), alpha = .1, shape = ".") +
    scale_alpha_identity() +
    scale_color_manual(
        values = setNames(
            cluscolmap$ClusCol,
            cluscolmap$Cluster
        ),
        guide = guide_legend(
            override.aes = list(shape = 19, alpha = 1)
        )
    ) +     
    facet_wrap(~sex) +
    theme_bw() +
    labs(x = "UMAP1", y = "UMAP2")
```

```{r}
residtab %>%
    map(
        mutate,
        fav_adip = (
            whr < 0 &
            sbp < 0 &
            dbp < 0 &
            fg < 0 &
            tg < 0 &
            ldl < 0 &
            hdl > 0 &
            crp < 0 &
            alt < 0 &
            scr < 0
        )
    ) %>%
    map(count, fav_adip) %>%
    map(mutate, prop = 100 * n/sum(n)) %>%
    bind_rows(.id = "sex")
```

```{r}
residtab %>%
    map(
        mutate,
        fav_adip = (
            whr < 0 &
            sbp < 0 &
            dbp < 0 &
            fg < 0 &
            tg < 0 &
            ldl < 0 &
            hdl > 0 &
            crp < 0 &
            alt < 0 &
            scr < 0
        )
    ) %>%
    imap(
        ~.x %>%
            select(fav_adip) %>%
            bind_cols(
                data.frame(
                    validclusmod$umapmod[validclusmod$sex == .y][[1]]$embedding
                )
            )
    ) %>%
    bind_rows(.id = "sex") %>%
    ggplot(aes(X1, X2)) +
    geom_point(alpha = .1, shape = ".") +
    geom_point(data = . %>% filter(fav_adip), size = .25, alpha = .25, color = "red") + 
    facet_wrap(~sex) +
    theme_bw() +
    labs(x = "UMAP1", y = "UMAP2")
```

# Generating a table of biomarkers for different levels of discordant probabilities

```{r}
newclus <- validclusmod %>%
    transmute(
        sex, 
        clusmod = map(
            clusmod, select, 
            Cluster = validclus_name
        )
    ) %>%
    unnest(clusmod)
newclus
```

```{r}
newclus <- newclus %>%
    nest(D = -sex) %>%
    mutate(
        D = map(
            D, 
            expand_grid, 
            ClusProf = Cluster,
            ProbLevel = c(.2, .4, .6, .8)
        )
    ) %>%
    unnest(D) %>%
    filter(ClusProf != "BC") %>%
    mutate(
        Weight = (
            ((Cluster == ClusProf) * ProbLevel) +
            ((Cluster == "BC") * (1 - ProbLevel))
        )
    ) %>%
    filter(Weight > 0) %>%
    arrange(sex, ClusProf, ProbLevel)
head(newclus)
```

```{r}
newclusres <- newclus %>%
    nest(D = -c(sex, ClusProf, ProbLevel)) %>%
    inner_join(validclusmod, by = "sex") %>%
    mutate(
        sex,
        D = map2(
            D, clusmod, 
            inner_join, 
            by = c("Cluster" = "validclus_name")
        ),
        D = map(
            D,
            ~MGMM::rGMM(
                n = 100000, 
                d = length(.x$validclus_centers[[1]]),
                k = nrow(.x),
                pi = .x$Weight,
                means = .x$validclus_centers, 
                covs = .x$validclus_covmats
            )
        ),
        D = map(D, colMeans),
        D = map2(D, clusmod, ~setNames(.x, names(.y$validclus_centers[[1]])))
    )
```

```{r}
newclusres <- newclusres %>%
    mutate(
        D = map2(
            D, residmod,
            ~tibble(
                Biomarker = names(.x), sdresidval = .x
            ) %>%
            inner_join(.y, by = "Biomarker") %>%
            mutate(
                sdresid = sdresidval * SDRes,
                bmi = 30 * bmi,
                age = 55 * age,
                bmvalue = rowSums(pick(Intercept, bmi, age, sdresid)),
                bmvalue = round(bmvalue, 2)
            ) %>%
            select(Biomarker, bmvalue) %>%
            pivot_wider(names_from = Biomarker, values_from = bmvalue)
        )
    ) %>%
    select(sex, ClusProf, ProbLevel, D) %>%
    unnest(D)
head(newclusres)
```

```{r}
newclusres %>%
    mutate(
        across(c(sbp, dbp), round)
    )
```
